---
title: "Title Goes Here"
author: "Names Go Here" 
output:
  html_document:
    theme: cerulean
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 3
    df_print: paged
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 3
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction
This data notebook contains the analysis that generated facts in the story ["Title"]() from the series ["Series"](). For each sentence in the story generated by original data analysis, we have provided the corresponding code and results.

## Load Libraries, Settings and Global Functions
```{r warning=FALSE,error=FALSE,message=FALSE}
# For general data science
library(tidyverse)

# For data cleaning
library(janitor)

# For loading Excel files
library(readxl)

# For working with datetime
library(lubridate)

# For U.S. Census Bureau data
library(tigris)

# For pretty tables
library(kableExtra)
library(knitr)

## Functions 

# Function for formatted table output

output_formatted_table = function(table, text){
  
  table %>% 
    kable(caption = text) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 14, fixed_thead = T) %>%
    scroll_box(width = "100%")
}


```
## Load Data

```{r}

# Load GT
etl_gt = readRDS("../data/processed/etl_gt_incident_log.rds")


# Load GWU
etl_gwu = readRDS("../data/processed/etl_gwu_incident_log.rds")


# Load Howard

etl_howard = readRDS("../data/processed/etl_howard_incident_log.rds")


# Load UMD
etl_umd_incident = readRDS("../data/processed/etl_umd_police_incident_data.rds")

etl_umd_arrest = readRDS("../data/processed/etl_umd_police_arrest_data.rds")


# Load GMU







```

##  Category break down

```{r}

# GT Category Breakdown
gt_incident_summary = etl_gt %>% 
  group_by(incident) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

## GWU Category Breakdown
gwu_incident_summary = etl_gwu %>% 
  group_by(nature_classification) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

## Howard Category Breakdown
howard_incident_summary = etl_howard %>% 
  group_by(natures_of_crimes) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

## UMD Incident Breakdown
umd_incident_summary = umd_incident_summary %>% 
  group_by() %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))


## UMD Arrest Breakdown


  


```




### Header

#### Subheader

```{r warning=FALSE,error=FALSE,message=FALSE}



```

## Analysis

### FACT: 

#### Explanation

#### Supporting code and output
```{r warning=FALSE,error=FALSE,message=FALSE}

```

-30-

